---
title: "Stardew Valley Fish part 2 - First Graphs"
author: "Valerie Whitfield"
output:
  html_document:
    theme: spacelab
    toc: false
  pdf_document:
    toc: false
---

^ I know I probably won't knit this Rmd, but it feels empty to not have that up there.

## Intro

Back at it again! This time I'll put my graph of fish catching times into an app so that I can easily filter by season and by location. 

## Loading everything in

Libraries...
```{r}
library(tidyverse)
library(shiny)
library(shinydashboard)
library(shinythemes)
```

Files...
```{r}
fish_df <- read_csv(file = "stardew_fish_tidy.csv")
```

## Prepping data

I could make a new variable for season
```{r}

```

And/or for whether the location is available to start (this one could be useful)
```{r}

```

But I don't think I need to for now, so I'll keep these blank. 

## App making

```{r}
ui <- fluidPage(    
  
  titlePanel("Stardew fish catching times"), # give the page a title
  
  # generate a row with a sidebar
  sidebarLayout(      
    
  # define the sidebar with one input
  sidebarPanel(
  checkboxGroupInput("selected_vars", "Select season:",
                         choices = c("spring", "summer", "fall", "winter"),
                         selected = "spring"), 
  selectInput("location", "Select location:", choices=c(unique(fish_df$location), "All"), selected = "Town River"),
              hr()),
    
  # create a spot for the barplot
  mainPanel(
  textOutput("test"))
  )
  )

  # define a server for the Shiny app
  server <- function(input, output, session) {
  
  # this stops the app upon closing
  session$onSessionEnded(stopApp)
      
  # fill in the spot we created for a plot
  output$test <- renderText({
    if (length(input$selected_vars) > 0) {
      filter_expr <- paste(input$selected_vars, "== TRUE", collapse = " | ")
      filter_expr <- str_c("(", filter_expr, ")")
      print(filter_expr)
    } else {
      "Please select at least one variable."
    }
    
    #class(input$location)
    #class(fish_df$location)
    
    #fish_df %>% 
      #{if (input$location != "All") {
        #filter(location == input$location) }}
  })
  }

shinyApp(ui, server)
```


Here goes nothing...

```{r, eval=F, echo=T}
ui <- fluidPage(    
  
  titlePanel("Stardew fish catching times"), # give the page a title
  
  # generate a row with a sidebar
  sidebarLayout(      
    
  # define the sidebar with one input
  sidebarPanel(
  checkboxGroupInput("selected_vars", "Select season:",
                         choices = c("spring", "summer", "fall", "winter"),
                         selected = "spring"), 
  selectInput("location", "Select location:", choices=c(unique(fish_df$location), "All"), selected = "Town River"),
              hr()),
    
  # create a spot for the barplot
  mainPanel(
  plotOutput("fishPlot", width="800px", height="800px"))
  )
  )

  # define a server for the Shiny app
  server <- function(input, output, session) {
  
  # this stops the app upon closing
  session$onSessionEnded(stopApp)
      
  # fill in the spot we created for a plot
  output$fishPlot <- renderPlot({
    if (length(input$selected_vars) > 0) {
      filter_expr <- paste(input$selected_vars, "== TRUE", collapse = " | ")
      filter_expr <- str_c("(", filter_expr, ")")
    } else {
      "Please select at least one variable."
    }
    
    times <- c("6am","7am","8am","9am","10am","11am","12pm","1pm","2pm","3pm","4pm","5pm","6pm","7pm","8pm","9pm","10pm","11pm","12am","1am","2am")
    
    fish_df %>% 
      filter(!!rlang::parse_expr(filter_expr)) %>% 
      {if (input$location != "All") filter(., location == input$location) else .} %>% 
      ggplot(aes(y=reorder(fish, desc(fish)), 
             xmin=start_time_hr, xmax=end_time_hr, color=weather))+
      geom_linerange(linewidth=3)+
      scale_x_continuous(breaks=0:20, labels=times, position="top")+
      labs(title="Fish catching times", y="Fish", x="Time")+
      theme(axis.text.x = element_text(size=10),
            axis.text.y = element_text(size=18),
            axis.title = element_text(size=15),
            title = element_text(size=20))
  })
  }

shinyApp(ui, server)
```

WAHOOO IT WORKS! I can now filter by location and season, and it's colored by weather. That's the most important thing.

## Next Steps

- Customize color palette
- Axis text bigger
